Exploring the Motives and Driving Forces Behind Modifications to APIs From a Software Evolution Perspective

### 2015-05-04 thesis/paper.tex
added structure for disc rq1.1

RQ1.1 - To what extent can we reverse engineer API change decisions?

While it is obvious that we did not manage to successfully categorise every single change, we did categorise a high enough percentage to form a solid conclusion; it is possible to reverse engineer the majority of change decisions using this categorisation technique.

>>>>

1. Added functionality or similar is easy to reverse engineer

2. It's hard to distinguish between maintainability/quality-related changes and refactoring/groomative-related changes

Bottom line: It is possible to reverse engineer to some extent
-While it is obvious that we did not manage to successfully categorise every single change, we did categorise a high enough percentage to form a solid conclusion; it is possible to reverse engineer the majority of change decisions using this categorisation technique.
